\documentclass[12pt,a4paper]{report}

% ============ PACKAGES ============
% 1. Document geometry and fonts
\usepackage{geometry}
\usepackage{fontspec}
\usepackage[vietnamese]{babel}

% 2. Math
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

% 3. Colors (must come before tikz, tcolorbox, listings)
\usepackage[dvipsnames,svgnames,x11names]{xcolor}

% 4. Graphics and diagrams
\usepackage{graphicx}
\usepackage{float}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{pdflscape}
\usepackage{rotating}

% 5. Tables
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{makecell}
\usepackage{diagbox}

% 6. Code and algorithms
\usepackage{listings}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

% 7. Boxes
\usepackage[most]{tcolorbox}

% 8. Layout and typography
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{indentfirst}
\usepackage[shortlabels]{enumitem}
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{chngcntr}
\usepackage{calc}
\usepackage{microtype}
\usepackage{perpage}
\usepackage{pifont}

% 9. hyperref LAST (standard LaTeX practice)
\usepackage{hyperref}

% TikZ libraries
\usetikzlibrary{
  arrows.meta,
  positioning,
  shapes.geometric,
  shapes.misc,
  fit,
  backgrounds,
  decorations.pathreplacing,
  calc,
  shadows,
  patterns,
  matrix,
  chains,
  mindmap,
  trees
}

% ============ FONTS ============
\IfFontExistsTF{TeX Gyre Termes}
  {\setmainfont[Ligatures=TeX]{TeX Gyre Termes}}
  {\setmainfont[Ligatures=TeX]{Latin Modern Roman}}
\IfFontExistsTF{TeX Gyre Cursor}
  {\setmonofont[Scale=0.85]{TeX Gyre Cursor}}
  {\setmonofont[Scale=0.85]{Latin Modern Mono}}
\IfFontExistsTF{TeX Gyre Heros}
  {\setsansfont[Ligatures=TeX]{TeX Gyre Heros}}
  {\setsansfont[Ligatures=TeX]{Latin Modern Sans}}

% ============ COLORS ============
\definecolor{bkblue}{RGB}{0,82,165}
\definecolor{bklightblue}{RGB}{219,234,254}
\definecolor{tier1col}{RGB}{30,58,95}
\definecolor{tier2col}{RGB}{59,31,110}
\definecolor{tier3col}{RGB}{26,77,26}
\definecolor{tier4col}{RGB}{92,45,0}
\definecolor{accentorange}{RGB}{234,88,12}
\definecolor{codegreen}{rgb}{0,0.55,0}
\definecolor{codegray}{rgb}{0.45,0.45,0.45}
\definecolor{codeblue}{rgb}{0.1,0.1,0.75}
\definecolor{codeback}{RGB}{248,248,252}
\definecolor{alertblue}{RGB}{219,234,254}
\definecolor{alertyellow}{RGB}{254,249,195}
\definecolor{alertred}{RGB}{254,226,226}
\definecolor{alertgreen}{RGB}{220,252,231}
\definecolor{rowgray}{RGB}{242,242,247}

% ============ LISTINGS (Python) ============
\lstdefinestyle{pythonstyle}{
    backgroundcolor=\color{codeback},
    commentstyle=\color{codegreen}\itshape,
    keywordstyle=\color{codeblue}\bfseries,
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{orange!80!black},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=6pt,
    showspaces=false,
    showstringspaces=false,
    tabsize=4,
    frame=single,
    framerule=0.5pt,
    rulecolor=\color{gray!40},
    language=Python,
    morekeywords={self,True,False,None,import,from,as,with,yield,lambda,assert,pass,raise,del,global,nonlocal,def,class,return,if,else,elif,for,while,break,continue,and,or,not,in,is,try,except,finally}
}
\lstset{style=pythonstyle}

% ============ GEOMETRY (BK standard) ============
\geometry{
    a4paper,
    left=3.5cm,
    right=2.0cm,
    top=2.5cm,
    bottom=3.0cm,
}

% ============ FONT SIZE & SPACING ============
\renewcommand{\normalsize}{\fontsize{13pt}{15.6pt}\selectfont}
\normalsize
\setlength{\parindent}{1.27cm}
\setlength{\parskip}{6pt}
\linespread{1.35}

% ============ CHAPTER / SECTION TITLES ============
\titleformat{\chapter}[display]
    {\centering\normalfont\fontsize{14}{17}\bfseries}
    {CHƯƠNG \thechapter}
    {4pt}
    {}
\titlespacing*{\chapter}{0pt}{-10pt}{20pt}

\titleformat{\section}
    {\normalfont\fontsize{13}{16}\bfseries}
    {\thesection}{0.6em}{}
\titlespacing*{\section}{0pt}{12pt}{6pt}

\titleformat{\subsection}
    {\normalfont\fontsize{13}{16}\bfseries\itshape}
    {\thesubsection}{0.5em}{}
\titlespacing*{\subsection}{0pt}{10pt}{4pt}

\titleformat{\subsubsection}
    {\normalfont\fontsize{13}{16}\itshape}
    {\thesubsubsection}{0.5em}{}
\titlespacing*{\subsubsection}{0pt}{8pt}{3pt}

% ============ COUNTERS ============
\counterwithin{figure}{chapter}
\counterwithin{table}{chapter}
% listings v1.11b defines lstlisting counter inside \AtBeginDocument,
% so we must defer our \counterwithin call likewise.
\makeatletter
\AtBeginDocument{%
  \@ifundefined{c@lstlisting}{}{\counterwithin{lstlisting}{chapter}}%
}
\makeatother
\MakePerPage{footnote}

% ============ PAGE STYLE ============
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\itshape Trường ĐH Bách Khoa -- ĐHQG TP.HCM}
\fancyhead[R]{\small\itshape Dự án STWI -- Hệ thống Điều phối Giao thông AI}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\setlength{\headheight}{16pt}

\fancypagestyle{plain}{
  \fancyhf{}
  \fancyfoot[C]{\thepage}
  \renewcommand{\headrulewidth}{0pt}
}

% ============ HYPERREF ============
\hypersetup{
    colorlinks=true,
    linkcolor=bkblue,
    citecolor=bkblue,
    urlcolor=codeblue,
    pdftitle={Bao cao Ky thuat Du an SmartTraffic What-If (STWI)},
    pdfauthor={Nhom STWI},
    bookmarksnumbered=true,
}

% ============ TCOLORBOX STYLES ============
\tcbset{
    notebox/.style={enhanced,colback=alertblue!40,colframe=codeblue!60,
        fonttitle=\bfseries\small,title=Ghi chú,left=4pt,right=4pt,top=3pt,bottom=3pt},
    warnbox/.style={enhanced,colback=alertyellow!60,colframe=orange!70!black,
        fonttitle=\bfseries\small,title=Cảnh báo,left=4pt,right=4pt,top=3pt,bottom=3pt},
    dangerbox/.style={enhanced,colback=alertred!50,colframe=red!65!black,
        fonttitle=\bfseries\small,title=Quan trọng,left=4pt,right=4pt,top=3pt,bottom=3pt},
    tipbox/.style={enhanced,colback=alertgreen!50,colframe=green!50!black,
        fonttitle=\bfseries\small,title=Mẹo kỹ thuật,left=4pt,right=4pt,top=3pt,bottom=3pt},
}

% ============ ALGORITHM2E ============
\SetAlgoLined
\SetKwInOut{Input}{Đầu vào}
\SetKwInOut{Output}{Đầu ra}
\SetKwComment{Comment}{/* }{ */}

% ============ PANDOC COMPAT ============
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\newcommand{\passthrough}[1]{#1}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

% ============ TIKZ GLOBAL STYLES ============
\tikzset{
  sysbox/.style={rectangle, rounded corners=4pt, draw=#1!70, fill=#1!15,
    text width=3.5cm, align=center, minimum height=1.2cm, font=\small\bfseries, text=#1!80!black},
  arrow/.style={-{Stealth[length=6pt]}, thick},
  dasharrow/.style={-{Stealth[length=6pt]}, thick, dashed},
  groupbox/.style={rectangle, rounded corners=6pt, draw=#1!60!black, fill=#1!8,
    dashed, line width=1.2pt},
  decnode/.style={diamond, draw=accentorange!80, fill=alertyellow!50, aspect=2.5,
    text width=2.8cm, align=center, font=\small\bfseries},
  procnode/.style={rectangle, rounded corners=3pt, draw=codeblue!70, fill=alertblue!30,
    text width=3.2cm, align=center, minimum height=0.9cm, font=\small},
  startend/.style={ellipse, draw=bkblue!70, fill=bklightblue!60,
    minimum width=2.2cm, minimum height=0.8cm, align=center, font=\small\bfseries},
}

\begin{document}

% ============================================================
% BÌA (TITLE PAGE)
% ============================================================
\begin{titlepage}
\newgeometry{left=1.8cm,right=1.8cm,top=1.5cm,bottom=1.5cm}

\begin{tikzpicture}[remember picture,overlay]
  \draw[bkblue,line width=2.8pt]
    ([shift={(0.8cm,-0.8cm)}]current page.north west)
    rectangle
    ([shift={(-0.8cm,0.8cm)}]current page.south east);
  \draw[bkblue,line width=0.6pt]
    ([shift={(1.05cm,-1.05cm)}]current page.north west)
    rectangle
    ([shift={(-1.05cm,1.05cm)}]current page.south east);
\end{tikzpicture}

\centering

\vspace*{0.4cm}
{\fontsize{14}{17}\selectfont\bfseries ĐẠI HỌC QUỐC GIA THÀNH PHỐ HỒ CHÍ MINH}\\[0.2cm]
{\fontsize{14}{17}\selectfont\bfseries TRƯỜNG ĐẠI HỌC BÁCH KHOA}\\[0.15cm]
{\fontsize{13}{16}\selectfont\bfseries KHOA KHOA HỌC VÀ KỸ THUẬT MÁY TÍNH}

\vspace{0.3cm}
{\color{bkblue}\rule{0.55\textwidth}{1.8pt}}

\vspace{0.8cm}

{\fontsize{14}{17}\selectfont\bfseries ĐỒ ÁN MÔN HỌC}\\[0.15cm]
{\fontsize{13}{16}\selectfont BÁO CÁO ĐẶC TẢ KỸ THUẬT TỔNG THỂ}

\vspace{0.9cm}

{\fontsize{19}{23}\selectfont\bfseries\color{bkblue}
SMARTTRAFFIC WHAT-IF\\[0.2cm] (STWI)}

\vspace{0.5cm}
{\color{bkblue!60}\rule{0.45\textwidth}{0.8pt}}
\vspace{0.4cm}

{\fontsize{14}{17}\selectfont\bfseries
HỆ THỐNG ĐIỀU PHỐI GIAO THÔNG THÔNG MINH\\[0.15cm]
SỬ DỤNG TRÍ TUỆ NHÂN TẠO ĐA TÁC TỬ\\[0.15cm]
VÀ COUNTERFACTUAL SAFETY LOOP LẤY CẢM HỨNG TỪ CF-VLA}

\vspace{1.1cm}

\begin{center}
\renewcommand{\arraystretch}{1.6}
\fontsize{12}{15}\selectfont
\begin{tabular}{ll}
  \textbf{Mã tài liệu:} & STWI-DOC-SYSTEM v2.0 \\
  \textbf{Phiên bản:}   & 2.0 (Bản chính thức) \\
  \textbf{Ngày xuất bản:} & \today \\
  \textbf{Trạng thái:}  & Bản đặc tả kỹ thuật hoàn chỉnh \\
  \textbf{Phân loại:}   & Tài liệu kỹ thuật dự án \\
\end{tabular}
\end{center}

\vspace{0.8cm}

\begin{center}
\renewcommand{\arraystretch}{1.5}
\fontsize{12}{15}\selectfont
\begin{tabular}{ll}
  \textbf{Nhóm thực hiện:}       & Nhóm Dự án STWI \\
  \textbf{Giảng viên hướng dẫn:} & TS. Nguyễn Văn A \\
  \textbf{Học kỳ:}               & Học kỳ 3 -- Năm học 2025--2026 \\
\end{tabular}
\end{center}

\vfill
{\fontsize{13}{16}\selectfont\itshape Thành phố Hồ Chí Minh -- \the\year}
\vspace{0.4cm}
\restoregeometry
\end{titlepage}

% ============================================================
% TÓM TẮT
% ============================================================
\newpage
\chapter*{TÓM TẮT}
\addcontentsline{toc}{chapter}{Tóm tắt}
\input{chapters/ch00_tom_tat}

% ============================================================
% MỤC LỤC / DANH MỤC
% ============================================================
\newpage
\tableofcontents

\newpage
\listoffigures
\addcontentsline{toc}{chapter}{Danh mục Hình vẽ}

\newpage
\listoftables
\addcontentsline{toc}{chapter}{Danh mục Bảng biểu}

% ============================================================
% DANH MỤC TỪ VIẾT TẮT
% ============================================================
\newpage
\chapter*{DANH MỤC CÁC TỪ VIẾT TẮT}
\addcontentsline{toc}{chapter}{Danh mục Từ viết tắt}
\input{chapters/ch00_abbreviations}

% ============================================================
% NỘI DUNG CHÍNH
% ============================================================
\newpage
\input{chapters/ch01_gioi_thieu}

\newpage
\input{chapters/ch02_co_so_ly_thuyet}

\newpage
\input{chapters/ch03_kien_truc}

\newpage
\input{chapters/ch04_data_pipeline}

\newpage
\input{chapters/ch05_ml_simulation}

\newpage
\input{chapters/ch06_rag}

\newpage
\input{chapters/ch07_agent}

\newpage
\input{chapters/ch08_implementation}

\newpage
\input{chapters/ch09_evaluation}

\newpage
\input{chapters/ch10_rui_ro}

% ============================================================
% KẾT LUẬN
% ============================================================
\newpage
\input{chapters/ch11_ket_luan}

% ============================================================
% TÀI LIỆU THAM KHẢO
% ============================================================
\newpage
\addcontentsline{toc}{chapter}{Tài liệu Tham khảo}
\begin{thebibliography}{99}

\bibitem{yu2018stgcn}
\textbf{B. Yu, H. Yin, Z. Zhu} (2018).
\textit{Spatio-Temporal Graph Convolutional Networks: A Deep Learning Framework for Traffic Forecasting}.
Proceedings of IJCAI 2018, pp.~3634--3640.

\bibitem{hochreiter1997lstm}
\textbf{S. Hochreiter, J. Schmidhuber} (1997).
\textit{Long Short-Term Memory}.
Neural Computation, 9(8), pp.~1735--1780.

\bibitem{li2018diffusion}
\textbf{Y. Li et al.} (2018).
\textit{Diffusion Convolutional Recurrent Neural Network: Data-Driven Traffic Forecasting}.
Proceedings of ICLR 2018.

\bibitem{kipf2017gcn}
\textbf{T. N. Kipf, M. Welling} (2017).
\textit{Semi-Supervised Classification with Graph Convolutional Networks}.
Proceedings of ICLR 2017.

\bibitem{wen2023surrogate}
\textbf{J. Wen et al.} (2023).
\textit{Neural Surrogate Models for Urban Traffic Simulation: A Comparative Study}.
Transportation Research Part C: Emerging Technologies, 150.

\bibitem{lakshminarayanan2017ade}
\textbf{B. Lakshminarayanan, A. Pritzel, C. Blundell} (2017).
\textit{Simple and Scalable Predictive Uncertainty Estimation using Deep Ensembles}.
Advances in NeurIPS 2017.

\bibitem{lewis2020rag}
\textbf{P. Lewis et al.} (2020).
\textit{Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks}.
Advances in NeurIPS 2020.

\bibitem{chen2023bge}
\textbf{J. Chen et al.} (2023).
\textit{BGE M3-Embedding: Multi-Lingual, Multi-Functionality, Multi-Granularity Text Embeddings Through Self-Knowledge Distillation}.
arXiv:2309.07597.

\bibitem{guo2023xiyansql}
\textbf{Y. Guo et al.} (2023).
\textit{XiYan-SQL: A Multi-Generator Ensemble Framework for Text-to-SQL}.
arXiv:2411.08599.

\bibitem{wooldridge2009multiagent}
\textbf{M. Wooldridge} (2009).
\textit{An Introduction to MultiAgent Systems}.
John Wiley \& Sons, 2nd edition.

\bibitem{langchain2023}
\textbf{H. Chase et al.} (2023).
\textit{LangChain: Building Applications with LLMs through Composability}.
GitHub Repository. \url{https://github.com/langchain-ai/langchain}.

\bibitem{pearl2018why}
\textbf{J. Pearl, D. Mackenzie} (2018).
\textit{The Book of Why: The New Science of Cause and Effect}.
Basic Books.

\bibitem{bjoern2021counterfactual}
\textbf{S. Beckers, J. Y. Halpern} (2021).
\textit{Causal Sufficiency and Actual Causation}.
Journal of Artificial Intelligence Research, 70, pp.~1--40.

\bibitem{zhang2020bytetrack}
\textbf{Y. Zhang et al.} (2022).
\textit{ByteTrack: Multi-Object Tracking by Associating Every Detection Box}.
Proceedings of ECCV 2022.

\bibitem{jocher2023yolo}
\textbf{G. Jocher et al.} (2023).
\textit{Ultralytics YOLOv8}.
GitHub Repository. \url{https://github.com/ultralytics/ultralytics}.

\bibitem{luong2019traffic}
\textbf{Q. T. Luong et al.} (2019).
\textit{Traffic Congestion Analysis and Simulation for Ho Chi Minh City}.
Journal of Transportation Engineering, 145(2).

\bibitem{milvus2021}
\textbf{J. Wang et al.} (2021).
\textit{Milvus: A Purpose-Built Vector Data Management System}.
Proceedings of SIGMOD 2021.

\bibitem{vanrossum2009python}
\textbf{G. Van Rossum, F. L. Drake} (2009).
\textit{Python 3 Reference Manual}.
CreateSpace, Scotts Valley, CA.

\bibitem{paszke2019pytorch}
\textbf{A. Paszke et al.} (2019).
\textit{PyTorch: An Imperative Style, High-Performance Deep Learning Library}.
Advances in NeurIPS 2019.

\bibitem{gtvt2023law}
\textbf{Bộ Giao thông Vận tải} (2023).
\textit{Luật Giao thông đường bộ (sửa đổi)}.
Nhà xuất bản Chính trị Quốc gia Sự thật.

\end{thebibliography}

% ============================================================
% PHỤ LỤC
% ============================================================
\appendix

\newpage
\chapter{Đặc tả API REST}
\input{chapters/appendix_api}

\newpage
\chapter{Cấu trúc Dữ liệu và Schema}
\input{chapters/appendix_schema}

\newpage
\chapter{Bộ Câu hỏi Kiểm thử Hệ thống}
\input{chapters/appendix_testcases}

\end{document}
